---
title: "Bayes Law applied to medical tests"
author: "Krish Arunasalam"
date: "2022-09-06"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Draw a graph of the probability of having a disease, given a positive
test, as a function of:

a.  the test sensitivity (true positive)
b.  the false positive rate
c.  the disease prevalence

Draw graphs a and b for a rare (1% prevalence) and common (10%
prevalence) disease. What do these graphs imply about the relative
importance of the various characteristics of medical tests?

``` {r}
p_disease <- c(0.01, 0.1)
p_no_disease <- 1 - p_disease
p_pos_g_disease <- seq(0.99, 0.01, -0.01)
p_neg_g_disease <- 1- p_pos_g_disease
p_pos_g_no_disease <- seq(0.01, 0.99, 0.01)
p_neg_g_no_disease <- 1 - p_pos_g_no_disease
```

Using the set probabilities let's compute the posterior probabilities:

``` {r}
posterior1 <- 0
posterior2 <- 0

posterior1 <- (p_pos_g_disease * p_disease[1])/(p_pos_g_disease * p_disease[1] + p_pos_g_no_disease * p_no_disease[1])

posterior2 <- (p_pos_g_disease * p_disease[2])/(p_pos_g_disease * p_disease[2] + p_pos_g_no_disease * p_no_disease[2])
```

Plotting the graphs in ggplot for section (a):

``` {r}
data <- data.frame('true_positive'=p_pos_g_disease, 'false_positive'=p_pos_g_no_disease,'pr_disease'=posterior1)
ggplot(data) +
  geom_line(aes(true_positive, pr_disease)) +
  geom_line(aes(false_positive, pr_disease)) +
  labs(title = 'For disease prevalence 0.01')
```

``` {r}
data <- data.frame('true_positive'=p_pos_g_disease, 'false_positive'=p_pos_g_no_disease,'pr_disease'=posterior2)
ggplot(data) +
  geom_line(aes(true_positive, pr_disease)) +
  geom_line(aes(false_positive, pr_disease)) +
  labs(title = 'For disease prevalence 0.1')
```